Data Builder

### 2019-04-05 notebooks/data_builder.Rmd
notebook w data

```{r}
# read in new one
psp_L0 <- read_csv("../data/partial_L0_subtype.csv")

# remove SUBTYPE rows
psp_L0 <- psp_L0[!psp_L0$pkg == "SUBTYPE",]
```

@@

```{r}
# read it back
psp <- read_csv("../data/partial_L1_subtype.csv")

>>>>

```{r}
# read in new one
psp_L0 <- read_csv("../data/partial_L0_subtype.csv.gz")
p
# remove SUBTYPE rows
psp_L0 <- psp_L0[!psp_L0$pkg == "SUBTYPE",]
```

@@

```{r}
# read it back
psp <- read_csv("../data/partial_L1_subtype.csv.gz")
